Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-08 Latex/tex/pr.tex
latex continue

@@

We want to solve \eqref{constraints1}. Since the problem is non-convex, iterative algorithm is applied.

@@

Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P} = \boldsymbol{P}_{max}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration. Two different method is applied to acquire $\boldsymbol{A}$. The first method is using MOSEK and second method is a heuristic algorithm.

@@

Using Lagrangian function and iterative algorithm, can solve this subproblem. 

>>>>

It is assumed that interference signal applied from UEs with same PRB.

@@

We want to solve \eqref{constraints1}. Since the problem is non-convex and NP-Hard iterative algorithm is applied.

@@

Firstly, we need to obtain $\boldsymbol{A}$ by fixing $\boldsymbol{P}$ in the problem \eqref{constraints1} and updating this parameter at the end of each iteration. Two different method is applied to acquire $\boldsymbol{A}$. The first method is using MOSEK and second method is a heuristic algorithm.

@@

This subproblem can  be solved using Lagrangian function and iterative algorithm. 
Since, Interference is a function of power of UEs, for simplicity, we assume an upper bound for interference (the worst-case) as follow
 \bar{I}_{u_{(v,i)}} &= 
 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{max} a_{vs}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{max}   a_{ys} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.\newline
Lagrangian function is written as follow
\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}} 
- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
&+\sum\limits_{s=1}^{S} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{d_{(s,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (C_{r_{(s,i)}}-C_{r_{(s,i)}}^{max}).\\ 
&- \sum\limits_{s=1}^{S}  \kappa_{r_{(s,i)}} (D_{s}-D_{s}^{max}).\\ 
